Portfolio conservation of metapopulations under\\climate change

### 2014-06-24 inst/ms/anderson-etal-metafolio.tex

%\begin{center}
%\includegraphics[width=2.9in]{../examples/thermal-curve-scenarios}
%\end{center}
\bigskip
\noindent
\textsc{Fig. 2}. Different ways of prioritizing response-diversity conservation. Panel a shows thermal tolerance curves for ten possible populations and panels b--e show different ways of prioritizing four of those populations. The curves describe how productivity varies with temperature for a given population. Some populations thrive at low temperatures (light greys) and some at warm temperatures (dark greys). Some are tolerant to a wider range of environmental conditions (mid greys) but with a lower maximum productivity. The total possible productivity (the area under the curves) is the same for each population.

@@

%\begin{center}
%\includegraphics[width=4.5in]{../examples/spatial-mv}
%\end{center}
\bigskip
\noindent
\textsc{Fig. 4}. The importance of preserving environmental response diversity through spatial conservation strategies. The conservation strategies correspond to figure 2 and represent conserving a range of responses (green), the most stable populations only (orange), or one type of environmental response (purple and pink). In risk-return space we show environmental scenarios that are comprised primarily of (a) short-term and (b) long-term environmental fluctuations. The dots show simulated metapopulations and the contours show 25\% and 75\% quantiles across 500 simulations per strategy. We also show example metapopulation abundance time series for the (c, e) short-term and (d, f) long-term environmental-fluctuation scenarios. The thick grey line (a, b) indicates the efficient frontier across all simulated metapopulations --- metapopulations with the minimum variability for a given level of growth rate.

@@

%\begin{center}
%\includegraphics[width=4.5in]{../examples/cons-plans-n}
%\end{center}
\bigskip
\noindent
\textsc{Fig. 5}. The importance of preserving as many populations as possible when we don't know how response diversity is distributed. In risk-return space we show environmental scenarios that are comprised primarily of (a) short-term and (b) long-term environmental fluctuations. We show metapopulations in which two through 16 populations of random response diversity are conserved. The dots show simulated metapopulations and the contours show 25\% and 75\% quantiles across 500 simulations per strategy. We also show example metapopulation (c) rate-of-change and (d) abundance time series for the short-term environmental-fluctuation scenario. The thick grey line (a, b) indicates the efficient frontier across all simulated metapopulations --- metapopulations with the minimum variability for a given level of growth rate.

\bigskip
\noindent
\textsc{Fig. 6}. Risk-return trade-off in the case where habitat is lost over time through stream flow reduction. The temperature follows both short-term fluctuations and a long-term increase. Response diversity is randomly conserved. Shading indicates conservation plans where two through 16 populations are conserved. (a) Conserving more populations decreases expected variance but also decreases expected growth rate. Dots show simulated metapopulations and contours show 25\% and 75\% quantiles across 500 simulations per strategy. The thick grey line indicates the efficient frontier across all simulated metapopulations --- metapopulations with the minimum variability for a given level of growth rate. Also shown are (b) example metapopulation growth rate and (c) abundance time series from the 2 and 16 population scenarios. Regression lines in (b) illustrate a decreasing growth rate through time.

@@

\begin{center}
\includegraphics[height=5.5in]{../examples/simulation-diagram3-sansserif-bw}\\
\textsc{Fig.} 1
\clearpage
\includegraphics[width=2.9in]{../examples/thermal-curve-scenarios}\\
\textsc{Fig.} 2
\clearpage
\includegraphics[width=4.0in]{../examples/spatial-arma-sim-full}\\
\textsc{Fig.} 3
\clearpage
\includegraphics[width=4.5in]{../examples/spatial-mv}\\
\textsc{Fig.} 4
\clearpage
\includegraphics[width=4.5in]{../examples/cons-plans-n}\\
\textsc{Fig.} 5
\clearpage
\includegraphics[width=3.0in]{../examples/cons-plans-squeeze}\\
\textsc{Fig.} 6
\clearpage
\end{center}

>>>>

%\begin{center}
%\includegraphics[width=2.9in]{../examples/thermal-curve-scenarios}
%\end{center}
\bigskip
\noindent
\textsc{Fig. 2}. Different ways of prioritizing thermal-tolerance conservation. Panel a shows thermal-tolerance curves for ten possible populations and panels b--e show different ways of prioritizing four of those populations. The curves describe how productivity varies with temperature for a given population. Some populations thrive at low temperatures (light greys) and some at warm temperatures (dark greys). Some are tolerant to a wider range of environmental conditions (mid greys) but with a lower maximum productivity. The total possible productivity (the area under the curves) is the same for each population.

@@

%\begin{center}
%\includegraphics[width=4.5in]{../examples/spatial-mv}
%\end{center}
\bigskip
\noindent
\textsc{Fig. 4}. The importance of preserving thermal-tolerance diversity through spatial conservation strategies. The conservation strategies correspond to figure 2 and represent conserving a range of responses (green), the most stable populations only (orange), or one type of environmental response (purple and pink). In risk-return space we show environmental scenarios that are comprised primarily of (a) short-term and (b) long-term environmental fluctuations. The dots show simulated metapopulations and the contours show 25\% and 75\% quantiles across 500 simulations per strategy. We also show example metapopulation abundance time series for the (c, e) short-term and (d, f) long-term environmental-fluctuation scenarios. The thick grey line (a, b) indicates the efficient frontier across all simulated metapopulations --- metapopulations with the minimum variability for a given level of growth rate.

@@

%\begin{center}
%\includegraphics[width=4.5in]{../examples/cons-plans-n}
%\end{center}
\bigskip
\noindent
\textsc{Fig. 5}. The importance of preserving as many populations as possible when we do not know how thermal-tolerance is distributed. In risk-return space we show environmental scenarios that are comprised primarily of (a) short-term and (b) long-term environmental fluctuations. We show metapopulations in which two through 16 populations are conserved. The dots show simulated metapopulations and the contours show 25\% and 75\% quantiles across 500 simulations per strategy. We also show example metapopulation (c) rate-of-change and (d) abundance time series for the short-term environmental-fluctuation scenario. The thick grey line (a, b) indicates the efficient frontier across all simulated metapopulations --- metapopulations with the minimum variability for a given level of growth rate.

\bigskip
\noindent
\textsc{Fig. 6}. Risk-return trade-off in the case where habitat is lost over time through stream flow reduction. The temperature follows both short-term fluctuations and a long-term increase. Thermal tolerance is randomly conserved. Shading indicates conservation plans where two through 16 populations are conserved. (a) Conserving more populations decreases expected variance but also decreases expected growth rate. Dots show simulated metapopulations and contours show 25\% and 75\% quantiles across 500 simulations per strategy. The thick grey line indicates the efficient frontier across all simulated metapopulations --- metapopulations with the minimum variability for a given level of growth rate. Also shown are (b) example metapopulation growth rate and (c) abundance time series from the 2 and 16 population scenarios. Regression lines in (b) illustrate a decreasing growth rate through time.

@@

\begin{center}
\includegraphics[height=5.5in]{../examples/simulation-diagram3-sansserif-bw}\\
\textsc{Fig.} 1
\clearpage
\includegraphics[width=2.4in]{../examples/thermal-curve-scenarios}\\
\textsc{Fig.} 2
\clearpage
\includegraphics[width=4.2in]{../examples/spatial-arma-sim-full}\\
\textsc{Fig.} 3
\clearpage
\includegraphics[width=4.5in]{../examples/spatial-mv}\\
\textsc{Fig.} 4
\clearpage
\includegraphics[width=4.5in]{../examples/cons-plans-n}\\
\textsc{Fig.} 5
\clearpage
\includegraphics[width=3.0in]{../examples/cons-plans-squeeze}\\
\textsc{Fig.} 6
\clearpage
\end{center}

### 2014-06-24 inst/ms/salmonfolios.tex

@@

\bibliographystyle{prsb}
\bibliography{jshort,ms}

@@

%\begin{center}
%\includegraphics[width=4.5in]{../examples/spatial-mv}
%\end{center}
\textbf{Figure 4.} The importance of preserving environmental response diversity through spatial conservation strategies. The conservation strategies correspond to Figure 2 and represent conserving a range of responses (green), the most stable populations only (orange), or one type of environmental response (purple and pink). In risk-return space we show environmental scenarios that are comprised primarily of (a) short-term and (b) long-term environmental fluctuations. The dots show simulated metapopulations and the contours show 25\% and 75\% quantiles across 500 simulations per strategy. We also show example metapopulation abundance time series for the (c, e) short-term and (d, f) long-term environmental-fluctuation scenarios. The grey line (a, b) indicates the efficient frontier across all simulated metapopulations --- metapopulations with the minimum variability for a given level of growth rate.

@@

%\begin{center}
%\includegraphics[width=4.5in]{../examples/cons-plans-n}
%\end{center}
\textbf{Figure 5.} The importance of preserving as many populations as possible when we don't know how response diversity is distributed. In risk-return space we show environmental scenarios that are comprised primarily of (a) short-term and (b) long-term environmental fluctuations. We show metapopulations in which 2 (red), 4 (orange), 8 (yellow), or 16 (green) populations of random response diversity are conserved. The dots show simulated metapopulations and the contours show 25\% and 75\% quantiles across 500 simulations per strategy. We also show example metapopulation (c) rate-of-change and (d) abundance time series for the short-term environmental-fluctuation scenario. The grey line (a, b) indicates the efficient frontier across all simulated metapopulations --- metapopulations with the minimum variability for a given level of growth rate

@@

\begin{spacing}{1.0}

\include{som}

>>>>

\newlabel{t:pars}{{S1}{3}}
\newlabel{f:stray}{{S1}{4}}
\newlabel{f:eg-sens}{{S2}{5}}
\newlabel{f:eg-sp-arma-full}{{S3}{6}}
\newlabel{f:eg-sp-arma-half}{{S4}{7}}
\newlabel{f:ret-corr}{{S5}{8}}
\newlabel{f:eg-sp-linear-full}{{S6}{9}}
\newlabel{f:eg-sp-linear-half}{{S7}{10}}
\newlabel{f:eg-n-arma-two}{{S8}{11}}
\newlabel{f:eg-n-arma-sixteen}{{S9}{12}}
\newlabel{f:eg-n-linear-two}{{S10}{13}}
\newlabel{f:eg-n-linear-sixteen}{{S11}{14}}

@@

\bibliographystyle{prsb}
\bibliography{jshort,ms}
%\input{salmonfolios.bbl}

@@

%\begin{center}
%\includegraphics[width=4.5in]{../examples/spatial-mv}
%\end{center}
\textbf{Figure 4.} The importance of preserving environmental response diversity through spatial conservation strategies. The conservation strategies correspond to figure 2 and represent conserving a range of responses (green), the most stable populations only (orange), or one type of environmental response (purple and pink). In risk-return space we show environmental scenarios that are comprised primarily of (a) short-term and (b) long-term environmental fluctuations. The dots show simulated metapopulations and the contours show 25\% and 75\% quantiles across 500 simulations per strategy. We also show example metapopulation abundance time series for the (c, e) short-term and (d, f) long-term environmental-fluctuation scenarios. The grey line (a, b) indicates the efficient frontier across all simulated metapopulations --- metapopulations with the minimum variability for a given level of growth rate.

@@

%\begin{center}
%\includegraphics[width=4.5in]{../examples/cons-plans-n}
%\end{center}
\textbf{Figure 5.} The importance of preserving as many populations as possible when we don't know how response diversity is distributed. In risk-return space we show environmental scenarios that are comprised primarily of (a) short-term and (b) long-term environmental fluctuations. We show metapopulations in which 2 (red), 4 (orange), 8 (yellow), or 16 (green) populations of random response diversity are conserved. The dots show simulated metapopulations and the contours show 25\% and 75\% quantiles across 500 simulations per strategy. We also show example metapopulation (c) rate-of-change and (d) abundance time series for the short-term environmental-fluctuation scenario. The grey line (a, b) indicates the efficient frontier across all simulated metapopulations --- metapopulations with the minimum variability for a given level of growth rate.

@@

\begin{spacing}{1.1}

\setcounter{page}{1}
\nolinenumbers
\include{som}

### 2014-06-24 inst/ms/tables.tex
Update files for Ecol Appl

\begin{table}[h!]
\centering
\footnotesize
\caption{Input parameters to the salmon metapopulation simulation with default values.}
\begin{tabular}{p{7.7cm}p{1.4cm}p{3.6cm}}
\toprule
Description                                                          & Symbol                & Value \\
\midrule

\textit{Population dynamics parameters}                              &                       & \\
Stock-recruit residual standard deviation (on log scale)             & $\sigma_r$            & 0.3  \\
AR(1) serial correlation of stock-recruit residuals                  & $\rho_w$              & 0.4  \\
Fraction of fish that stray from natal streams                       & $f_{\mathrm{stray}}$  & 0.02  \\
Exponential rate of decay of straying with distance                  & $m$                   & 0.3  \\

\noalign{\vskip 3mm}
\textit{Environmental parameters}                                    &                       & \\
Width of environmental-tolerance curves for populations $i$ 1 to $n$ & $W_i$                 & Sequence of 0.05 to 0.02 to 0.05\\
Optimum environmental value for populations $i$ 1 to $n$             & $e_i^{\mathrm{opt}}$  & Sequence of 13 to 19\\
Area under each environmental-tolerance curve in environmental units & $A$                   & 30\\

Standard deviation of short-term environmental fluctuations          & $\sigma_d$            & 2 \\
AR(1) autocorrelation of short-term environmental fluctuations       & $\rho_e$              & 0.1 \\
Slope of long-term environmental signal                              & $\beta_e$             & 0.114 \\

\noalign{\vskip 3mm}
\textit{Fishery parameters}                                          &                       & \\
Standard deviation of beta distribution for implementation error     & $\sigma_{h}$          & 0.05  \\
Frequency of assessment (years)                                      & $f_{\mathrm{assess}}$ & 5  \\
\bottomrule
\end{tabular}
\label{t:pars}
\end{table}
\clearpage

>>>>

% TODO check that these values are all still correct - some aren't

\begin{table}[h!]
\centering
\footnotesize
\caption{Input parameters to the salmon metapopulation simulation with default values.}
\smallskip
\begin{tabular}{>{\RaggedRight}p{7.8cm}p{1.1cm}p{2.5cm}>{\RaggedRight}p{3.3cm}}
\toprule
Description                                                          & Symbol                & Value                  & Reference  \\
\midrule

\bibpunct{}{}{;}{a}{}{}
\textit{Population dynamics parameters}                              &                       &                        &             \\
Stock-recruit residual standard deviation (on log scale)             & $\sigma_r$            & 0.7                    & \citep{thorson2014a}  \\
AR(1) serial correlation of stock-recruit residuals                  & $\rho_w$              & 0.4                    & \citep{thorson2014a}  \\
Fraction of fish that stray from natal streams                       & $f_{\mathrm{stray}}$  & 0.02                   & \citep{quinn2005} and references therin  \\
Exponential rate of decay of straying with distance                  & $m$                   & 0.1                    & \citep{cooper1999}      \\
Range of maximum productivities                                      & $a_i^{\mathrm{max}}$  & 2.2--2.9             &  \citep{dorner2008}   \\

\noalign{\vskip 3mm}
\textit{Environmental parameters}                                    &                       &                        &             \\
Width parameter for thermal-tolerance curves for populations $i$ 1 to $n$  (values generate widths in line with listed references) & $W_i$                 & 0.08--0.04--0.08       &  \citep{brett1952, eliason2011}           \\
Optimum environmental value for populations $i$ 1 to $n$             & $e_i^{\mathrm{opt}}$  & 13--19                 &  \citep{eliason2011}           \\
%Area under each environmental-tolerance curve in environmental units & $A$                  & 30                     &             \\
Standard deviation of annual temperature fluctuations          & $\sigma_d$            & 2                      & \citep{eliason2011}      \\
AR(1) autocorrelation of annual temperature fluctuations       & $\rho_e$              & 0.1                    &             \\
Annual increase in stream temperature in degrees Celcius             & $\beta_e$             & 0.04                   & \citep{mantua2010}     \\

%TODO cite Mantua 2010 in main text

\noalign{\vskip 3mm}
\textit{Fishery parameters}                                          &                       &                        &             \\
Standard deviation of beta distribution for implementation error     & $\sigma_{h}$          & 0.1                    & \citep{pestes2008}            \\
Frequency of assessment (years)                                      & $f_{\mathrm{assess}}$ & 5                      &             \\
\bottomrule
\end{tabular}
\label{t:pars}
\end{table}
\clearpage
\bibpunct{(}{)}{;}{a}{}{}
